\bf The EPEC Model

### 2021-09-28 Documentation/EPEC_Model.tex
Added TOFF and electromagnetic torque plots

>>>>

\subsection{Glasser-Greene-Johnson Data}
Let us write
\begin{equation}
{\bf B} = \nabla\phi\times\nabla\psi_p+g(\psi_p)\,\nabla\phi.
\end{equation}
The angle $\theta^{\,\ast}$ is defined such that
\begin{equation}
\nabla\phi\times\nabla\psi_p\cdot\nabla\theta^{\,\ast} = \gamma(\psi_p)\,B.
\end{equation}
Let
\begin{align}
J_1(\psi_p) &= \oint\frac{1}{B}\,\frac{d\theta^{\,\ast}}{2\pi},\\[0.5ex]
J_2(\psi_p) &= \oint B\,\frac{d\theta^{\,\ast}}{2\pi},\\[0.5ex]
J_3(\psi_p) &= \oint\frac{1}{B^{\,3}}\,\frac{d\theta^{\,\ast}}{2\pi},\\[0.5ex]
J_4(\psi_p) &= \oint\frac{1}{B\,|\nabla\psi_p|^{\,2}}\,\frac{d\theta^{\,\ast}}{2\pi},\\[0.5ex]
J_5(\psi_p) &= \oint\frac{B}{|\nabla\psi_p|^{\,2}}\,\frac{d\theta^{\,\ast}}{2\pi},\\[0.5ex]
J_6(\psi_p) &= \oint\frac{1}{B^{\,3}\,|\nabla\psi_p|^{\,2}}\,\frac{d\theta^{\,\ast}}{2\pi}.
\end{align}
It follows that
\begin{align}
E(\psi_p) &= - \frac{dP/d\psi_p}{(dq/d\psi_p)^{\,2}}\,\frac{1}{\gamma}\left[\frac{d}{d\psi_p}\!\left(\frac{J_1}{\gamma}\right) - g\,\frac{dq}{d\psi_p}\,\frac{J_1}{J_2}\right]J_5,\\[0.5ex]
F(\psi_p) &= \frac{(dP/d\psi_p)^{\,2}}{(dq/d\psi_p)^{\,2}}\,\frac{1}{\gamma^{\,2}}\left[g^{\,2}\left(J_5\,J_6- J_4^{\,2}\right)+ J_5\,J_3\right],
\\[0.5ex]
H(\psi_p)&= \frac{dP/d\psi_p}{dq/d\psi_p}\,\frac{g}{\gamma}\left(J_4 - \frac{J_1\,J_5}{J_2}\right),
\end{align}
where $P(\psi_p)$ is the total plasma pressure. 
Finally,
\begin{equation}
D_R(\psi_p)= E + F + H^{\,2}.
\end{equation}
